Data Encryption Standard Implementation 4003-482-01 RIT

### 2010-05-06 paper/paper.tex
Team contributions section.

\section{Original Runtime Measurements}
\paragraph{}Each test consisted of 1,000,000 encryptions of the message 123456789ABCDEF and key 133457799BBCDFF1. They were performed on a 1.8 Ghz Core2Duo computer running Ubuntu 10.04.
\\Test 1:
\\ \indent 10.856 seconds
\\Test 2:
\\ \indent 10.885 seconds
\\Test 3:
\\ \indent 10.912 seconds
\\\\Average:
\\ \indent 10.884 seconds
\section{Original Runtime Analysis}
\section{Revised Software design}
\section{Revised Runtime Measurements}
\paragraph{}Each test consisted of 1,000,000 encryptions of the message 123456789ABCDEF and key 133457799BBCDFF1. They were performed on a 1.8 Ghz Core2Duo computer running Ubuntu 10.04.
\\Test 1:
\\ \indent 5.294 seconds
\\Test 2:
\\ \indent 5.321 seconds
\\Test 3:
\\ \indent 5.385 seconds
\\\\Average:
\\ \indent 5.333 seconds
\section{Revised Runtime Analysis}
\section{Developers manual}
\section{Users Manual}

@@

  There also exist a few small for loops in the code which might benifit slightly from being unrolled.
  We chose not to unroll them because in our profiling they didn't seem to be a problem. Also to unroll
  these left over loops would affect the readability of the code tremendously, many things would need to be 
  restructured. However unrolling all the loops might achive a slight speed up to the overall speed of implementation.
  The difference mostly depends on the quality of the optimizations being performed by the compiler.

@@

>>>>

\section{Original Runtime Measurements}
\paragraph{}Each test consisted of 1,000,000 encryptions of the message 123456789ABCDEF and key 133457799BBCDFF1. They were performed on a 1.8 Ghz Core2Duo computer running Ubuntu 10.04.
\\Test 1:
\\ \indent 10.899 seconds
\\Test 2:
\\ \indent 10.867 seconds
\\Test 3:
\\ \indent 10.870 seconds
\\\\Average:
\\ \indent 10.879 seconds
\section{Original Runtime Analysis}
\section{Revised Software design}
\section{Revised Runtime Measurements}
\paragraph{}Each test consisted of 1,000,000 encryptions of the message 123456789ABCDEF and key 133457799BBCDFF1. They were performed on a 1.8 Ghz Core2Duo computer running Ubuntu 10.04.
\\Test 1:
\\ \indent 5.960 seconds
\\Test 2:
\\ \indent 6.012 seconds
\\Test 3:
\\ \indent 5.903 seconds
\\\\Average:
\\ \indent 5.958 seconds
\section{Revised Runtime Analysis}
\section{Developers manual}
\section{Users Manual}

@@

  There also exist a few small for loops in the code which might benefit slightly from being unrolled.
  We chose not to unroll them because in our profiling they didn't seem to be a problem. Also to unroll
  these left over loops would affect the readability of the code tremendously, many things would need to be 
  restructured. However unrolling all the loops might achieve a slight speed up to the overall speed of implementation.
  The difference mostly depends on the quality of the optimizations being performed by the compiler.

@@

  At the start of the project we divided up th major parts of the cipher implementation for each person to do. \\

  \textbf{Brian:}
  \begin{itemize}
    \item Unit test setup
    \item Build system
    \item Gathering of all constants and permutation blocks.
    \item Key schedule 
    \item Main DES algorithm
  \end{itemize}

  \textbf{Sam:}
  \begin{itemize}
    \item Bit operators and converters
    \item Feistel function
    \item Implementation API design
    \item Mix function to handle mixing
    \item Block mode implementation
  \end{itemize}

  Once these tasks were complete we worked together to integrate all parts together and debug our final product. Most of this
  time was spent pair programming. The presentation and this paper were split up similarly but much of the work was done together, 
  working cooperatively.
